Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
Mention Condorcet and STV.

\pv\ also aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
a fair election.

@@

>>>>

\pv\ \cite{preta} also aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
a fair election.

@@

Note that this ballot form supports alternative voting methods, such as Condorcet and Single Transferable Vote, in which voters rank candidates in order of preference rather than voting for a single candidate.
